Deriving Multi-Headed Projective Dependency Parses \\ from Link Grammar Parses

### 2014-06-03 doc/LinksToDAG.tex
very minor

For our analysis of these parses, we further discarded those that had dropped words, where the link parser could not attach links to every word in the sentence. About \input{figure/conll_analysis_sentences_dropped}of the non-disconnected sentences were removed, leaving us working only with complete link parses.

>>>>

For our analysis of these parses, we further discarded those that had dropped words, where the link parser could not attach links to every word in the sentence. About \input{figure/conll_analysis_sentences_dropped} of the non-disconnected sentences were removed, leaving us working only with complete link parses.
